\cventry{\texttt{C}\newline
\texttt{Python}\newline
\texttt{TCP}\newline
\texttt{MPTCP}\newline
\texttt{tc}\newline
\texttt{Kernel}\newline
}{Multipath TCP (MPTCP) for Dual-band WiGig (802.11ad)/WiFi (802.11ac) networks}{}{}{}{
\begin{itemize}
  \item Leveraged MPTCP to engage two network interfaces simultaneously in an application-transparent manner.
  \item Instrumented MPTCP (Linux 4.x) using \texttt{kernel probes} to monitor over 32 parameters in real-time.
  \item Instrumented TCP/MPTCP send and recv queues to track input and output timestamp for each byte.
  \item Used observations to design a new MPTCP packet scheduler - \underline{AMuSe} to improve overall throughput.
  \item Implemented AMuSe as a kernel module replacing the default MPTCP scheduler and exposed userspace controls.
  \item Evaluated AMuSe extensively which showed up to \textbf{2.5x} throughput improvement over the default scheduler.
  \item Submitted a top-tier conference paper (under review).
\end{itemize}
}

\cventry{\texttt{C}\newline
\texttt{Python}\newline
\texttt{expect}\newline
\texttt{select}\newline
\texttt{Socket API}\newline
}{Programming Assignments and Automated Grader for the computer-networking course}{}{}{\link[\faGithub]{https://cse4589.github.io}}{
\begin{itemize}
  \item Designed and developed set of three networking programming assignments (PAs) along with an automated tester/grader, now standard in the CSE department at UB for the networking course.
  \item Developed the auto-grader as a distributed application that fully automates the entire process of packaging, uploading and grading student submissions over a real network of five servers.
  \item PA 1: Text Chat \& File Transfer Application \link[\faExternalLink]{https://cse4589.github.io/pa1/} (Source: \link[\faGithub]{https://github.com/swetanksaha/cse4589-pa1})
        \begin{itemize}
          \item Introduces basic socket programming, client-server model and use of \texttt{select} syscall.
          \item Test cases check understanding of the byte-stream model of TCP (vs. UDP's packet-based).
          \item Bonus file-transfer components allows students to compare file I/O vs. network I/O.
        \end{itemize}
  \item PA 2: Reliable Transport Protocols \link[\faExternalLink]{https://cse4589.github.io/pa2/} (Source: \link[\faGithub]{https://github.com/swetanksaha/cse4589-pa2})
        \begin{itemize}
          \item Uses a simulated environment to ask students to implement three reliable data transport protocols.
          \item Requires implementation of multiple alarms with a single simulator timer.
          \item Modified an existing simulator to add sanity checks and internal support for different test cases.
        \end{itemize}
  \item PA 3: Software Defined Routing \link[\faExternalLink]{https://cse4589.github.io/pa3/} (Source: \link[\faGithub]{https://github.com/swetanksaha/cse4589-pa3})
        \begin{itemize}
          \item Involves implementation of a simplified version of the distance vector routing protocol (using UDP).
          \item Introduces students to the concept of control and data planes asking them to implement both functionalities.
          \item Requires contruction of raw packets in code using techniques akin to the Linux kernel (Sample code: \link[\faGithub]{https://github.com/swetanksaha/cse4589-pa3/blob/master/SampleCode/swetankk/src/control_header_lib.c}).
        \end{itemize}
\end{itemize}
}
