\cventry{\textit{Summer 2017}\newline
\texttt{C}\newline
\texttt{Python}\newline
\texttt{OpenWRT}\newline
}{Research Associate (Intern)}{\textbf{Hewlett Packard Enterprise (HPE) Labs}}{Palo Alto, CA}{US}{
\underline{LTE-Unlicensed/WiFi Co-existence in 5 GHz for WiFi Access Points (APs)}
\begin{itemize}
  \item Designed a WiFi (802.11ac)-based mechanism - DeMiLTE for enterprise APs to combat LTE-U/LAA interference.
  \item Developed software to detect, quantify and react to LTE interference in real time, without extra AP hardware.
  \item Implemented DeMiLTE inside the AP firmware making it light-weight and eliminating need for client modifications.
  \item Evaluated DeMiLTE in a real network showing it improves AP downlink throughput by up to \textbf{110\%}.
  \item Published 1 top-tier conference paper and filed 1 patent.
\end{itemize}
}

\cventry{\textit{Summer 2016}\newline
\texttt{C}\newline
\texttt{Python}\newline
\texttt{Drivers}\newline
\texttt{LEDE}\newline
}{Research Intern}{\textbf{IMDEA Networks Institute}}{Madrid}{Spain}{
\underline{Millimeter-wave Networking}
\begin{itemize}
  \item Analyzed performance issues in next-generation of WiFi: 60 GHz (802.11ad)-based indoor WLANs.
  \item Instrumented the Linux wireless device driver (wil6210) to export PHY/MAC information to userspace. \link[\faGithub]{https://github.com/swetanksaha/wil6210}
  \item Modifed the Linux wil6210 driver to allow user control over PHY parameters, like beam direction.
  \item Undertook an extensive measurement study with the instrumented APs and laptops to study 802.11ad links.
  \item Highlighted novel challenges and provided insights for practical aspects like coverage and AP deployment.
  \item Published the results of the study in a top-tier conference.
\end{itemize}
}

\cventry{\textit{Summer 2013}\newline
\texttt{Python}\newline
\texttt{Java}\newline
\texttt{Android}\newline
\texttt{Django}\newline
}{Software Developer}{\textbf{Google Summer of Code 2013}}{Google}{}{
\underline{\link[Funf]{https://www.funf.org/}: Open sensing and data collection framework for Android (acquired by Google)} \link[\faGithub]{https://github.com/funf-org/funf-inabox}
\begin{itemize}
  \item Improved Funf-in-a-box (FIAB), a service for users to build custom data collection app with zero programming.
  \item Ported the entire FIAB service from a always-on architecture running on a single EC2 serve to on-demand VM instantiation on Google cloud in 1 month, greatly reducing costs \& increasing performance. \link[\faExternalLink]{https://opensource.googleblog.com/2013/08/who-is-new-in-google-summer-of-code_30.html}
  \item Added support for configuring and deploying custom surveys and capturing additional user input.
\end{itemize}
}

\cventry{\textit{Summer 2012}\newline
\texttt{Android}\newline
\texttt{Ubuntu Juju}\newline}{Research Intern}{\textbf{Airbus India, EADS Innovation Works}}{Bangalore}{India}{
\underline{Image based localization techniques}
\begin{itemize}
  \item Built an indoor localization service that uses image features to estimate position of an Android device.
  \item Implemented as a distributed system offloading image processing to a remote system accessed through an API.
  \item Packaged and deployed the system as a Juju charm for easy deployment and scalability.
\end{itemize}
}

\cventry{\textit{2013--Present}}{Research Assistant}{University at Buffalo, SUNY}{NY}{US}{}

\cventry{\textit{2013--Present}}{Teaching Assistant}{University at Buffalo, SUNY}{NY}{US}{}
%Designed and developed assignments and automated grader for the Modern Networking Concepts course\newline\httplink[https://cse4589.github.io/]{https://cse4589.github.io/} [\link[Github Source]{https://github.com/cse4589}]
